\documentclass[a4paper]{article}

\input{Preamble}
\fancyhead[c]{Agenda}
\titlelabel{}

\begin{document}

\section{Agenda}

\ss{April 29th}

\section{Minutes}

\ss{April 15th}

\begin{enumerate}
  \item Status
    \begin{itemize}
      \item Grammar for propositions is implemented as mutually recursive 
      datatypes in SML

      \item Conversion to \f{string} is implemented for propositions
      
      \item Conversion to symbol syntax (\emph{not} \s{BoxProver}) is
      implemented for formulas

      \item Conversion of formulas to propositions is implemented
    \end{itemize}

  \item Discussion points
    \begin{description}
      {\color{DarkGrey}
      \item[Question:] Should quotation marks alternate between `p' and 
      ``p''?

      \item[Question:] Should disjunctions be negated with 'neither/nor'
      constructions?

      \item[Question:] Are non-bracketed implications fine as elements in
      lists, or should they be bracketed?

      \item[Question:] Are non-bracketed implications fine as final elements
      in \s{and also} constuctions? See result of tests for reference.

      \item[Question:] When an \s{and} list starts with an \s{and}-pair, 
      should this be split into two elements (which is what happens now), 
      or should the pair be kept as the first element?

      \item[Question:] Do bracketed statements and negations work in
      \s{pair}-constructions, or should \f{SINGLE} be exchanged for 
      \f{UNIT}?

      \item[Question:] Are we satisfied with how the propositions read in
      general? See result of tests for reference.}

    \end{description}

  \item Action items
    \begin{enumerate}[\HollowBox]
      \item[\CrossedBox] Update natural language proposition grammar 
      to account for the fact that
      implications only take \f{UNIT} and \f{NEGATION}, not \f{STAT}
      \item[\CrossedBox] Update natural language proposition grammar to 
      account for decisions
      \item \textcolor{Red}{Extend} \textcolor{Green}{Write} natural
      language grammar to proofs
        \begin{enumerate}[\HollowBox]
          \item Account for rules
          \item Account for references
          \item Account for preamble
        \end{enumerate}
    \end{enumerate}

  \item Misc
    \begin{description}
      \item[Decision:] At least for now, render formulae in symbol notation
      and focus on doing the proof steps in natural language.

      \item[Decision:] Create an "inclusive" rather than restrictive syntax 
      for proofs: it is important for the program to accept incorrect 
      proofs in order to correct the syntax. In other words: if students are
      to learn, they need to make mistakes.
    \end{description}
\end{enumerate}

\label{LastBody}
\end{document}
